Pre-processing high frequency animal tracking data

### 2020-08-25 01_background.Rmd
update bg with do smoove fun

```{r sim_smoove_data}
# define parameters
nu <- 2
tau <- 1
dt <- .01 
ucvm1 <- simulateUCVM(nu = nu, tau = tau, T.max = 100, dt = dt)

# get the data in data.table format
data <- as.data.table(ucvm1$XY)

# rescale coordinates
data[, c("x", "y") := (lapply(.SD, 
                          scales::rescale)),
     .SDcols = c("x", "y")]

# add a time column
data[, time := seq_len(nrow(data))]

@@

# plot real and introduced error
ggplot(d2)+

  geom_path(aes(x_error, y_error),
            col = "red", size = 0.2)+
  geom_path(aes(x, y))##+
  geom_path(data = data, aes(x, y),
            col = "blue")

>>>>

```{r sim_smoove_data}
do_smoove_data <- function(t_max = 100, dt = dt) {
  # define parameters
  nu <- 2
  tau <- 1
  dt <- .01 
  ucvm1 <- smoove::simulateUCVM(nu = nu, tau = tau, T.max = 100, dt = dt)

  # get the data in data.table format
  tmp_data <- data.table::as.data.table(ucvm1$XY)
  # rescale coordinates
  tmp_data[, c("x", "y") := (lapply(.SD, 
                                scales::rescale)),
       .SDcols = c("x", "y")]

  # add a time column
  tmp_data[, time := seq_len(nrow(tmp_data))]

  return(tmp_data)
}
```

```{r save_data}
data <- do_smoove_data()

@@

# plot real and introduced error
ggplot()+
  geom_path(data = data, aes(x, y),
            col = "blue")
